Manuscript

### 2015-02-05 inst/simulation/manuscript.Rmd
...

prettyScenario <- function(scenario) substr(scenario, 1, 1)
prettyModelName <- function(x) {
  lookup <- data.frame(x=modelNames, y=c("ST", "TF", "T", "FMP"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

@@

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated >= overEstimate) / nrow(x)) * 100)
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed, MeanProp=NA, SDProp=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(x$Estimated/x$Observed)
    prop.sd <- sd(x$Estimated/x$Observed)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), Failed=failed, MeanProp=prop.mean, SDProp=prop.sd))
  }, overEstimate=overEstimate)

@@

  z <- z[,c("Scenario","Model","Slope","R2","Failed","MeanProp","SDProp")]
  #z$EstDev <- round(z$EstDev, 2)
  z$MeanProp <- round(z$MeanProp, 2)
  z$SDProp <- round(z$SDProp, 2)
  if (!missing(file)) write.csv(z, file=file)
  return(z)
}

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp;

@@

dir <- normalizePath(context$figuresDirectory)
write.csv(logTable1, file=file.path(dir, "table-1a.csv"))
write.csv(logTable2, file=file.path(dir, "table-2a.csv"))
write.csv(logTable3, file=file.path(dir, "table-3a.csv"))
```

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersections <- plyr::join(populationSizes, intersections)
intersections2000 <- plyr::join(populationSizes2000, intersections2000)
intersections10days <- plyr::join(populationSizes10Days, intersections10days)
i.stat <- function(x) data.frame(i.mean=round(mean(x$intersections/x$Observed),2), i.sd=round(sd(x$intersections/x$Observed),2))
ddply(intersections, .(Scenario), i.stat)
ddply(intersections2000, .(Scenario), i.stat)
ddply(intersections10days, .(Scenario), i.stat)
```

>>>>

prettyScenario <- function(scenario) substr(scenario, 1, 1)
prettyModelName <- function(x) {
  lookup <- data.frame(x=modelNames, y=c("ST", "VT", "T", "FMP"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

@@

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated >= overEstimate) / nrow(x)) * 100)
    if (x$modelName == "FMPModel") failed <- NA
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed, MeanProp=NA, SDProp=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(x$Estimated/x$Observed)
    prop.sd <- sd(x$Estimated/x$Observed)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), MeanProp=prop.mean, SDProp=prop.sd, Failed=failed))
  }, overEstimate=overEstimate)

@@

  z <- z[,c("Scenario","Model","Slope","R2","MeanProp","SDProp","Failed")]
  #z$EstDev <- round(z$EstDev, 2)
  z$MeanProp <- round(z$MeanProp, 2)
  z$SDProp <- round(z$SDProp, 2)
  if (!missing(file)) write.csv(z, file=file)
  return(z)
}

writeTable <- function(df, filename, context) {
  library(ReporteRs)
  doc <- docx()
  flextable <- FlexTable(df)
  addFlexTable(doc, flextable)
  dir <- normalizePath(context$figuresDirectory)
  writeDoc(doc, file=file.path(dir, filename))
}

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp; 
logTable1

@@

subset(logTable1, Model != "VT")
subset(logTable2, Model != "VT")
subset(logTable3, Model != "VT")

#dir <- normalizePath(context$figuresDirectory)
#write.csv(logTable1, file=file.path(dir, "table-1a.csv"))
#write.csv(logTable2, file=file.path(dir, "table-2a.csv"))
#write.csv(logTable3, file=file.path(dir, "table-3a.csv"))

writeTable(subset(logTable1, Model != "VT"), "table-1a.docx", context)
writeTable(subset(logTable2, Model != "VT"), "table-1b.docx", context)
writeTable(subset(logTable3, Model != "VT"), "table-1c.docx", context)
```

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersections <- plyr::join(populationSizes, intersections)
intersections2000 <- plyr::join(populationSizes2000, intersections2000)
intersections10days <- plyr::join(populationSizes10Days, intersections10days)
i.stat <- function(x) data.frame(o.mean=mean(x$Observed), o.sd=sd(x$Observed), e.mean=mean(x$Estimated), e.sd=sd(x$Estimated),
                                 pp.mean=round(mean(x$Estimated/x$Observed), 2), pp.sd=round(sd(x$Estimated/x$Observed), 2),
                                 i.mean=mean(x$intersections), i.sd=sd(x$intersections), ip.mean=round(mean(x$intersections/x$Observed),2), ip.sd=round(sd(x$intersections/x$Observed),2))
ddply(intersections, .(Scenario, modelName), i.stat)
ddply(intersections2000, .(Scenario, modelName), i.stat)
ddply(intersections10days, .(Scenario, modelName), i.stat)
```
